\chapter{Synopsis}
\paragraph{}
Chess is a two-player strategy board game played on a chessboard, a checkered gameboard with 64 squares arranged in an 8×8 grid. Each player begins with 16 pieces: one king, one queen, two rooks, two knights, two bishops, and eight pawns. Each of the six piece types moves differently, with the most powerful being the queen and the least powerful the pawn. The objective is to checkmate the opponent's king by placing it under an inescapable threat of capture. We intend to implement the game of Chess in Java with a Graphical User Interface using Java Swing Library. The Java Swing Library uses Java's features such as Multithreading and Inheritance to enable flexible construction of User Interfaces.

\section{Problem Definition}
\paragraph{}
Chess is a board game involving two players.There are two sides,one using the white pieces and the other using the black pieces.Each of the sets of pieces includes:
\newline  1. One King
\newline  2. One Queen
\newline  3. Two Rooks
\newline  4. Two Bishops
\newline  5. Two Knights
\newline  6. Eight pawns

All of these pieces have their own distinct moves their own moves.
Each player plays alternately,with white always moving first.A piece cannot be moved to another square if it is already occupied,unless it is an opponent's piece in which case the opponent's piece is removed off the board.
The goal of the game is to strategize and place the opponent's king in an inescapable position and thus become the winner, while also protecting one's own king.If a conclusion cannot be reached, the game can also be declared as a draw.Given a 8*8 chessboard and the current configuration of the board as input, the code should be able to display all the possible legal moves for a selected piece.

\section{Objective}

The objective was to design a simple GUI based chess game which can be played by two users alternately,allowing them to make legal moves, utilizing the Object-Oriented Programming features of Java. During the course of the game,for a selected piece, all it's possible legal moves should be shown to the user.The game should also display when a king is under threat and when the game ends.The game should mimic the official game of chess as closely as possible.The goal was also to design a user-friendly game with a simple interface.Also the details of the players are also to be stored , including his win/loss statistics.Also the duration of the time the game can be played was also to be preset.The goal was to simulate a real chess game as closely as possible. The input to the core of the program is the 8 by 8 chessboard and the current configuration of the chess board,and the output is to present the users with all the possible legal moves for a selected piece. A visual GUI makes the input/output interaction very easy 